### 2016-09-29 rebuttal.tex

Emphasize that the environment variable \texttt{SYMPY\_DEBUG} must be set before importing SymPy for the first time.
\begin{solution}
Footnote~\ref{S-suppnote:gruntz} was added right before the final example from the Gruntz algorithm section.
\end{solution}

@@

\question In line 183, syntax \texttt{symbols(\textquotesingle{}a:d\textquotesingle{})} is used without being previously defined or explained.
\begin{solution}
Now we use \texttt{symbols(\textquotesingle{}a b c d\textquotesingle{})}, like in other places.
\end{solution}

\question Figure 2 should not be a screenshot, but rather proper code with \LaTeX-rendered results and explanations, as was done in the rest of the paper. A
 shortened link to SymPy Gamma for the example's expression can be included
 for the user to try this for themselves.
\begin{solution}
We believe this is not a good idea.  This figure is meant to be an archival
capture, not software subject to being re-rendered. SymPy Gamma currently only
renders as HTML\@. SymPy Gamma doesn't export output as \LaTeX{} or other external
formats.

A link to the project site was added to the text ``SymPy Gamma''. The text for
the figure caption now links to the page that generated it.
\end{solution}

### 2016-09-30 introduction.tex
Better word
Add sentence for projects that depend on SymPy to intro
Wording

As a library, SymPy does not have a built-in graphical user interface (GUI).
However, SymPy exposes a rich interactive display system, and supports
registering display formatters with Jupyter~\cite{kluyver2016jupyter} frontends,
including the Notebook and Qt Console, which will render SymPy expressions
using MathJax~\cite{cervone2012mathjax} or \LaTeX{}.

The remainder of this paper discusses key components of the SymPy library.
Section~\ref{sec:features} enumerates the features of SymPy and takes a closer
look at some of the important ones. The section~\ref{sec:numerics} looks at
the numerical features of SymPy and its dependency library, mpmath.
Section~\ref{sec:domain_specific} looks at the domain specific physics
submodules for performing symbolic and numerical calculations in classical
mechanics and quantum mechanics. Section~\ref{sec:architecture} discusses the
architecture of SymPy. Conclusions and future directions for SymPy are given
in section~\ref{sec:conclusion}. All examples in this paper use SymPy version
1.0 and mpmath version 0.19.

@@

All the examples in this paper can be tested on
\href{http://live.sympy.org}{SymPy Live}, an online Python shell that uses the
Google App Engine~\cite{ciurana2009google} to execute SymPy code. SymPy Live
is also integrated in the SymPy documentation at
\href{http://docs.sympy.org}{http://docs.sympy.org}.

>>>>

Being a library, SymPy does not have a built-in graphical user interface (GUI).
However, SymPy exposes a rich interactive display system, and supports
registering display formatters with Jupyter~\cite{kluyver2016jupyter} frontends,
including the Notebook and Qt Console, which will render SymPy expressions
using MathJax~\cite{cervone2012mathjax} or \LaTeX{}.

The remainder of this paper discusses key components of the SymPy library.
Section~\ref{sec:features} enumerates the features of SymPy and takes a closer
look at some of the important ones. The section~\ref{sec:numerics} looks at
the numerical features of SymPy and its dependency library, mpmath.
Section~\ref{sec:domain_specific} looks at the domain specific physics
submodules for performing symbolic and numerical calculations in classical
mechanics and quantum mechanics. Section~\ref{sec:architecture} discusses the
architecture of SymPy. Section~\ref{sec:other-proj} looks at a selection of
packages that depend on SymPy. Conclusions and future directions for SymPy are given
in section~\ref{sec:conclusion}. All examples in this paper use SymPy version
1.0 and mpmath version 0.19.

@@

All the examples in this paper can be tested on
\href{http://live.sympy.org}{SymPy Live}, an online Python shell that uses the
Google App Engine~\cite{ciurana2009google} to execute SymPy code. SymPy Live
is also integrated into the SymPy documentation at
\href{http://docs.sympy.org}{http://docs.sympy.org}.
